Turbulence in compact to giant HII regions

### 2022-03-17 strucfunc_paper.tex
Javier changes 2022-03-16

The results obtained with equation \ref{eq:Br} are use in a non-linear least-squares fit with the equation \ref{eq:sf-functional} used as an objective function.
For this purpose we use the \textit{python} package \textit{lmfit} \citep{newville_matthew_2014_11813} where the equation \ref{eq:Br} and \ref{eq:sf-functional} are use in a chi-square statistic defined as:
%
%\begin{equation}\label{eq:chi}
%  \chi^2 = \sum_i ^N \frac{[y_i^{\text{measure}}-y_i^{\text{model}} (\boldsymbol{v})]^2}{\epsilon_i ^2}
%\end{equation}
%
%
\begin{equation}\label{eq:chi}
  \chi^2 = \sum_i ^N \frac{[B(r)-B_{\text{func}}(r;r_0, \sigma^2\pos, m, s_0, B_{\text{noise}})]^2}{\varepsilon_i ^2}
\end{equation}
%
where the turbulent parameters are \(r_{0}\)\ , \(\sigma^2\pos\) and \(m\), and the observational constraints \(s_0\) and \( B_{\text{noise}}\).
This procedure calculate a value \(\chi\) to be minimized scaled by the inverse of the uncertainty \(\varepsilon\) in the data.
To obtain the confidence intervals we use the minimization procedure \textit{emcee} \citep{2013PASP..125..306F} which is a \textit{python} implementation of the affine-invariant ensemble sampler for Markov chain Monte Carlo (MCMC) by \citet{2010CAMCS...5...65G}.  
%Using these procedure we obtain the posteriors for our model and the parameters in equation~\ref{eq:chi}.

%In this way we want to avoid one fundamental problem in the interpretation of the structure function. 
%The slope in the majority of previous studies and hence, the correlation length, is obtained without a formal procedure. 
%The traditional way to find the correlation length it is to determine a particular range of ascending values in the structure function. 
%If this increase in values is stopped or reversed it is commonly assumed that one particular inertial range has been found. 
%In some cases this procedure keeps going up to large scales, giving two or more inertial regimes leading to an erroneous interpretation of multiple inertial scales.

>>>>

The results obtained with equation \ref{eq:Br} are use in a non-linear least-squares fit with the equation \ref{eq:sf-functional} used as an objective function.
For this purpose we use the \textit{python} package \textit{lmfit} \citep{newville_matthew_2014_11813} where the equation \ref{eq:Br} and \ref{eq:sf-functional} are use in a chi-square statistic defined as:
%
%\begin{equation}\label{eq:chi}
%  \chi^2 = \sum_i ^N \frac{[y_i^{\text{measure}}-y_i^{\text{model}} (\boldsymbol{v})]^2}{\epsilon_i ^2}
%\end{equation}
%
%
\begin{equation}\label{eq:chi}
  \chi^2 = \sum_i ^N \frac{[B(r)-B_{\text{func}}(r;r_0, \sigma^2\pos, m, s_0, B_{\text{noise}})]^2}{\varepsilon_i ^2}
\end{equation}
%
where the turbulent parameters, \(r_{0}\)\, \(\sigma^2\pos\) and \(m\), and the observational constraints \(s_0\) and \( B_{\text{noise}}\), are the set of variables to be optimized in the fit.
This procedure calculate a value \(\chi\) to be minimized scaled by the inverse of the uncertainty \(\varepsilon\) in the data.
Then we proceed to obtain the confidence intervals we use the minimization procedure \textit{emcee} \citep{2013PASP..125..306F} which is a \textit{python} implementation of the affine-invariant ensemble sampler for Markov chain Monte Carlo (MCMC) by \citet{2010CAMCS...5...65G}.
